### 2021-05-25 paper/paper_risk.tex
Added the case of several currencies.

@@

	% older stuff
	\bibitem{matrixanalysis} Roger A. Horn, Charles R. Johnson, \emph{Matrix Analysis}, 2nd Edition, Cambridge University Press, 2013.
	\bibitem{schur} J. Schur, Über Potenzreihen, die im Innern des Einheitskreises beschränkt sind, Journal für die reine und angewandte Mathematik \textbf{147}, 205 -- 232, 1917.
	\bibitem{bana} T. Banachiewicz, Zur Berechnung der Determinanten, wie auch der Inversen, und zur darauf basierten Auflösung der Systeme linearer Gleichungen, Acta Astronom. S\'er. C 3, 41--67, 1937.
	\bibitem{frazer} Frazer, R., Duncan, W., Collar, A. (1938). Elementary Matrices And Some Applications To Dynamics And Differential Equations, Cambridge University Press, 1938.
	\bibitem{ouellette} Ouellette, D. (1981). Schur complements and statistics Linear Algebra and its Applications  36, 187-295. https://dx.doi.org/10.1016/0024-3795(81)90232-9
	\bibitem{albert} Albert, A. (1969). Conditions for Positive and Nonnegative Definiteness in Terms of Pseudoinverses SIAM Journal on Applied Mathematics  17(2), 434-440. https://dx.doi.org/10.1137/0117041
	\bibitem{smith} Smith, R. (2008). The positive definite completion problem revisited Linear Algebra and its Applications  429(7), 1442-1452. https://dx.doi.org/10.1016/j.laa.2008.04.020	
	\bibitem{roger} Penrose, R. (1955). A generalized inverse for matrices Mathematical Proceedings of the Cambridge Philosophical Society  51(3), 406-413. https://dx.doi.org/10.1017/s0305004100030401
\end{thebibliography}

>>>>

\section{Several currencies}
In the previous section we have just looked at one foreign currency $A$ with one exchange rate $X$. The procedure can easily be extended to an arbitrary number of foreign currencies. We will denote the foreign currencies by a capital letter:
\begin{equation}
	A, B, C, \ldots
\end{equation}
The exchange rate between the domestic currency $E$ and the foreign currency $A$ will now be denoted by 
\begin{equation}
	X_E^A.
\end{equation}
If $m_A$ is an amount in currency $A$ then $X_E^Am_A$ is the corresponding amount in currency $E$. If we are given the same correlation coefficients as in the previous section we obtain the graph in figure \ref{fig.several}. The corresponding graph of cliques is shown in figure \ref{fig.severalCliques}.

\begin{figure}[hbt]
  \begin{center}
  	\includegraphics[width=10cm]{img/severalCurrencies.png}
  \end{center}
  \caption{The graph corresponding to the incomplete correlation matrix for five foreign currencies.}\label{fig.several}
\end{figure}

\begin{figure}[hbt]
  \begin{center}
  	\includegraphics[width=12cm]{img/severalCurrCliques.png}
  \end{center}
  \caption{The graph of cliques for the case of several foreign currencies. A clique tree is obtained by removing the lighter edges in the middle layer. It is again a tree of height two.}\label{fig.several}
\end{figure}

@@

\end{thebibliography}
